In this section, we go over prequisites to use {\pubs}. None of those require any
particularly intensive computation power, and they can be all installed on a 
personal laptop.

\subsection{Operating System And Software}
As {\pubs} does not require a compilation, it is expected to work on any operating system (OS).
That being said, some functionality of underlying {\python} does depend on the kernel. 
The author has not tested on Windows family OS, and he highly doubt it would work on it. 
There should be no problem on Unix and Linux family OS. 

We use {\git} for a software repository and version control. As mentioned, {\pubs} use
{\php}, {\psql}, and {\python}. A summary of minimaum version for these software is given
below. These are oldest version that the author happened to find on his machines, so it
is possible that things work on even older version of kernel/software. Please tell the 
author or update the document if you find such case.

\begin{itemize}
\item Supported Operating Systems
    \begin{itemize}
    \item Mac OSX 10.5.8 (Darwin 9.8) or later with Xcode 3.1.4 or later
    \item Linux 2.6.0 or later with \gpp 4.1 or later
    \end{itemize}
\item Version Control Tool
    \begin{itemize}
    \item {\git} $\ldots$ 1.7.1 or later
    \end{itemize}
\item Base Software Tools
    \begin{itemize}
    \item {\php} $\ldots$ v2.1 or later
    \item {\psql}$\ldots$  v9.1 or later with {\ttfamily contrib} for {\hstore}
    \item {\python} $\ldots$ v2.7 or later (but no later than 3.0)
    \item {\psycopg} $\ldots$ v2.5 or later
    \end{itemize}
\end{itemize}
Both recent OSX and Linux distributions have {\python} 2.7 and {\git}. So we skip
those items. The next section discuss how to install some rather uncommon parts
including {\psql}, {\hstore}, and {\psycopg}.

Both {\psql} and {\python} has a very good documentation and FAQ resource on the web.
You may find Ref.\cite{PythonDoc,PSQLDoc} useful.
